One exact and one random sampling method to assess the reliability of inferences from network enrichment analysis

### 2018-05-07 doc/genesetdp.tex
text

We implemented a Python program that reads network and pathway definition files and scored query sets against a pathway according to Equation \ref{eq:sum_i}, using GeneSetDP and GeneSetMC described in the Algorithm section, that enabled us to assign $p$~values according to Equation \ref{eq:pval}. We downloaded pathway and network definitions from the BinoX's website and used the same network threshold as BinoX default ($0.7$).

@@

\begin{figure}[htb]
  \begin{center}
      \includegraphics[width=1.0\textwidth]{figures/calibration_multiple.png}
  \end{center}
  \caption{{\bf Calibration of GeneSetDP and GeneSetMC.} We selected 10000 random sets of 10, 20 and 30 genes from the investigated genome definition and calculated their $p$ values with GeneSetMC and GeneSetDP against the ``Glycolysis/Gluconeogenesis'' pathway. To test the $p$~values uniformity we plotted them against their normalized rank. We also added the calibration curve of BinoX, evaluated on the same random sets.}
  \label{fig:calibration}
\end{figure}

>>>>

We implemented a Python program that reads network and pathway definition files and scores a query sets against a pathway according to Equation \ref{eq:sum_i}, using GeneSetDP and GeneSetMC described in the Algorithm section, that enabled us to assign $p$~values according to Equation \ref{eq:pval}. We downloaded pathway and network definitions from the BinoX's website and used the same network threshold as BinoX default ($0.7$).

@@

\begin{figure}[htb]
  \begin{center}
      \includegraphics[width=1.0\textwidth]{figures/calibration_multiple.png}
	  % \includegraphics{figures/calibration_legend.png}
  \end{center}
  \caption{{\bf Calibration of GeneSetDP and GeneSetMC.} We selected 10000 random sets of 10, 20 and 30 genes from the investigated genome definition and calculated their $p$ values with GeneSetMC and GeneSetDP against the ``Glycolysis/Gluconeogenesis'' pathway. To test the $p$~values uniformity we plotted them against their normalized rank. We also added the calibration curve of BinoX, evaluated on the same random sets. On all plots the dashed line shows $y = x$ and the dotted lines $y = 2x$ and $y = 0.5x$, for comparison}
  \label{fig:calibration}
\end{figure}
